Model to study co-evolution of trade an culture

### 2015-03-24 article.tex
fixed references

\begin{figure*}[htb]
{
\centering
Jean-Marc Montanier\\
Simon Carrignon\\ 
Xavier Rubio\\
\vspace{12pt}
Barcelona Supercomputing Center\\
Carrer de Jordi Girona, 29, \\
08034 Barcelona, Spain\\
}
\end{figure*}

@@

\xrc{what is exactly the definition of culture used in the paper? I would suggest this one: \emph{Culture is socially learned information capable of affecting  individual phenotypes. People acquire culture from other  individuals, via teaching or imitation} \cite{richerson1996}}

@@

The variation mechanisms are at the heart of the creation of the creation of new cultural elements~\cite{obrien_variation_1990}. These may happen due to some errors during the copy process~\cite{schillinger_copying_2014}. In more recent culture we can witness the apparition of mutations with intentionality~\cite{ziman_technological_2003}\xrc{see also recombination \cite{sole_2013}}.

>>>>

\begin{figure*}[htb]
{
\centering
Jean-Marc Montanier\\
Simon Carrignon\\ 
Xavier Rubio-Campillo\\
\vspace{12pt}
Barcelona Supercomputing Center\\
Carrer de Jordi Girona, 29, \\
08034 Barcelona, Spain\\
}
\end{figure*}

@@

\xrc{what is exactly the definition of culture used in the paper? I would suggest this one: \emph{Culture is socially learned information capable of affecting  individual phenotypes. People acquire culture from other individuals, via teaching or imitation} \cite{richerson_1996}}

@@

The variation mechanisms are at the heart of the creation of the creation of new cultural elements~\cite{obrien_variation_1990}. These may happen due to some errors during the copy process~\cite{schillinger_copying_2014}. In more recent culture we can witness the apparition of mutations with intentionality~\cite{ziman_2003}\xrc{see also recombination \cite{sole_2013}}.
